manuscript

### 2023-12-08 manuscript.rmd
Update manuscript.rmd
added language about Tweedie distributions

@@

|------------------|------------------|--------------------|------------------|

>>>>

"The Tweedie is a family of exponential type distributions, which are tolerant to large numbers of zero observations (Candy 2004)." -- Lacey and Hammond 2023

(Candy, S.G. 2004. Modeling catch and effort data using Generalised Linear Models, the Tweedie Distriution, Random Vessel Effects and Random Stratum-by-Year effects. CCAMLR Sci. 11: 59--80.)

@@

|------------------------------------|------------------|---------------------------------------------------------------------------------------------------------------------------------------------------|-----------------------------------------|
